Anomalous waves triggered by abrupt depth changes: experimental measurements and deterministic-statistical truncated KdV theory

### 2019-10-04 paper2_JNLS/paper.tex
NM

We will primarily consider the case in which waves originate from a region of constant depth, encounter an abrupt depth change, and then continue in another region of constant depth. Thus, depth will be piecewise constant
\begin{align}
\depth = 
\begin{cases}
\dup \quad \mbox{if } x<0 \\
\ddn \quad \mbox{if } x>0
\end{cases}
\end{align}
Most often, we will consider waves moving into shallower depth, so that $\dup > \ddn$.

>>>>

As in the experiments, we consider waves that originate from a region of constant depth, encounter an abrupt depth change, and continue in another region of constant depth. Thus, depth will be piecewise constant
\begin{align}
\depth = 
\begin{cases}
\dup \quad \mbox{if } x<0 \\
\ddn \quad \mbox{if } x>0
\end{cases}
\end{align}
Most often, we will consider waves moving into shallower depth, so that $\dup > \ddn$.
